Verification of concurrent design patterns with data

### 2019-02-07 2018-Arch-pNets/arch-pNets.tex
Updated title and abstract

\title{BIP Architectures and Open pNets}

\author{%
Simon~Bliudze\inst{1}
\and
Ludovic~Henrio\inst{2}
\and
Eric~Madelaine\inst{3}
\and
...
}

@@

\begin{abstract}
  We extend the theory of architectures with a general
  mechanism for handling various types of data transfer.  We
  encode this extended model into the open pNet semantic
  model and show how this encoding can be used to verify
  that an architecture does, indeed, enforce its
  characteristic property.

\keywords{}
\end{abstract}

>>>>

\title{Verification of concurrent design patterns with data}

\author{%
Simon~Bliudze\inst{1}
\and
Ludovic~Henrio\inst{2}
\and
Eric~Madelaine\inst{3}
}

@@

\begin{abstract}
We provide a solution for the design of safe concurrent systems by
compositional application of verified design patterns\mdash which we
call \emph{architectures}\mdash to a minimal set of functional
components.  To this end, we extend the theory of architectures
developed previously for the BIP framework with the elements necessary
for handling data: definition and operations on data domains, syntax
and semantics of composition operators involving data transfer.  Under
monotonicity assumptions on guards and assignments, composition of
architectures preserves their characteristic safety properties.

To verify that individual architectures do enforce their associated
properties, we provide a non-trivial encoding into an intermediate
model called open pNets that supports SMT-based verification.
Additionally, the translation into the open pNet semantic model gives
us a strong insight and a comparison of the coordination mechanisms
provided by the two frameworks.  The approach is illustrated by a case
study based on a previously developed BIP model of a nanosatellite
on-board software.

\keywords{Parametrised verification, composition, safety, interaction
  models.}
\end{abstract}
